### 2013-02-18 inst/doc/nonparametric-bayes.Rmd
reorganize content

Non-parametric approaches to optimal policy are more robust
===========================================================

@@

Carl Boettiger, Marc Mangel, Steve Munch

# Abstract

# Introduction

@@

# Approach and Methods

@@

# Discussion / Conclusion

@@

## Future directions

@@

# Appendix / Supplementary Materials

## MCMC posterior distributions and convergence analysis

>>>>

% Carl Boettiger; Marc Mangel; Steve Munch
% Non-parametric approaches to optimal policy are more robust

@@

Abstract
=======================================================================

Introduction
=======================================================================

@@

Approach and Methods
=====================================================================

@@

Discussion / Conclusion
==================================================================

@@

Future directions
--------------------------------------------------------------------

@@

Acknowledgments
================

This work was partially supported by the Center for Stock Assessment Research, a partnership between the University of California Santa Cruz and the Fisheries Ecology Division, Southwest Fisheries Science Center, Santa Cruz, CA and by NSF grant EF-0924195 to MM.

Appendix / Supplementary Materials
==================================

MCMC posterior distributions and convergence analysis
----------------------------------------------------------------------------
